\Russell's Metatheoretic Study - Abstract

### 2006-05-31 papers/slides-ICFP'06/abstract-only.tex
Add some bib, draft of abstract for ws

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{xspace} % To get the right spacings in front of : and so on
\usepackage[english]{babel}
\usepackage{abbrevs}
\usepackage{subfigure}
\usepackage{ifthen}
\usepackage{coqdoc}
\usepackage{bussproofs}
\usepackage{pgf,pgfarrows,pgfnodes}

\title{\Russell's metatheoretic study}
\date{}
\begin{document}
\maketitle
\abstract
\input{abstract}
\myabstract
\end{document}

>>>>

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{xspace} % To get the right spacings in front of : and so on
\usepackage[english]{babel}
\usepackage{abbrevs}
\usepackage{subfigure}
\usepackage{ifthen}
\usepackage{coqdoc}
\usepackage{bussproofs}
\usepackage{pgf,pgfarrows,pgfnodes}
\usepackage{concmath}
\usepackage{url}
\usepackage{fullpage}

\title{\Russell's Metatheoretic Study - Abstract}
\date{\today}
\author{Matthieu Sozeau \\
  LRI - Paris Sud - XI University \\
  sozeau@lri.fr}
\begin{document}
\maketitle

We are working on the formalization of \Russell{}'s type theory in the
\Coq{} proof assistant \cite{sozeau:coq/Russell/meta}.
The type system of \Russell{} is based on the
Calculus of Constructions with $\Sigma$-types (dependent sums), extended by an equivalence on types
which subsumes $\beta$-conversion. The extension permits to identify
types and subsets based on them in a manner similar to the
\emph{Predicate Subtyping} feature of \PVS{}. We are aiming at 
a complete proof of \Russell{} metatheoretic properties (structural
properties, Subject Reduction, maybe Strong Normalization), the
refining steps which
led us to the algorithmic system and the corresponding typing algorithm and also the correctness of a
traduction from \Russell{} to the Calculus of Inductive Constructions
with metavariables.

We started the development using the formalization of the
Calculus of Constructions by Bruno Barras \cite{Barras96a}.
We kept the standard de Bruijn encoding for variable bindings and
defined our judgements using \emph{dependent} inductive predicates.
This alone causes some problems for the faithful formalization of the
paper results.  
The proofs offer several other technical difficulties including:
\begin{itemize}
\item Elimination of transitivity in a system with an \emph{untyped} type
  conversion relation.

\item Subject Reduction, which is \emph{not} directly provable for the
  declarative system. Here we adapted the technique developped by
  Robin Adams \cite{adams:PTSEQ}. It includes a new term algebra, with
  associated reduction operations and a new type system
  for which we have to prove metatheoretic properties.

\item Correction of the traduction: the target system include
  metavariables, introducing a second, \emph{unusual} kind of variable binding.
\end{itemize}

We will present these difficulties and our recipes for solving them in
the \Coq environment. Additionaly, we will identify more general problems for
proving in \Coq and suggest possible solutions.

{\bf Disclaimer}: this is a work in
progress ; to this day we have proved elimination of transivity and
subject reduction should follow soon.

\bibliography{bib-joehurd,barras,pvs-bib,bcp,Luo,biblio-subset,%
cparent,demons,demons2,demons3}
\bibliographystyle{acm}

%% \renewcommand{\thefootnote}{}
%% \footnotetext{This article was typeset in \LaTeX~using the
%%   \texttt{Concrete Math} font}

\end{document}
